Evolved disk population of young brown dwarfs in \emph{Ophiuchus}\footnote{This paper includes data gathered with the 6.5 meter Magellan Telescopes located at Las Campanas Observatory, Chile.}

### 2015-05-05 chIMACS/ms.tex
This section is related to issue 56 in the paper (BAADE)
incorporate most of AJW comments all the way to the end

Of the 530 slits on the seven slit masks (Table \ref{tbl_IMACSslitMasks}), 505 spectra passed through spectral reduction with \texttt{Cosmos}.  The other 25 were not reduced either because they fell on chip gaps, were irretrievable, or were reserved for future analysis.

@@

\subsection{Spectral classification with \emph{The Hammer}}
We visually inspected the IMACS $I-$band spectra for evidence of broad-band molecular absorption in the region $6500<\lambda(\angstrom)<9000 $.  The broad FeH, VO, and TiO bands are characteristic of late M spectral types, and are conspicuous even in smoothed ($R\sim100$) low signal-to-noise ratio ($S/N > 5$) spectra.  To accelerate the process of visually classifying hundreds of spectra, we employed Version 1.2.5 of \emph{The Hammer} spectral typing code \citep{2007AJ....134.2398C,2011AJ....141...97W}.  \emph{The Hammer} first computes a machine spectral type based on several spectral type sensitive indices.  Then \emph{The Hammer} overlays user-selectable comparison spectra, which can be visually matched to the overall spectral shape.  \emph{The Hammer} does not have a mechanism for tuning the extent of wavelength-dependent extinction, so since some of our sources are reddened, matches to the observed spectra may lead us to overestimate the spectral type.  This overestimate is okay, since we only use this first pass as a coarse filter for both signal-to-noise ratio ($S/N >5$), and overall spectral shape (consistent with M0 or later).  If not, we discard the spectrum from our follow up sample.  If so, we assign a coarse spectral type that we will later use to coarsely estimate the extinction.

@@

More than half of the spectra that were rejected had $S/N < 8$.  About 5 of these rejects were due to the most egregious cases of instrumental artifacts in the MOS spectral mapping.  In those cases, we went back to visually inspect the 2D trace to convince ourselves that the traces were inconsistent with M or L spectral types.  Slitmask \texttt{ophwes} (Table \ref{tbl_IMACSslitMasks}) exhibited a large fraction of unusable spectra since since it only received $\sim45$ minutes of on-sky observing time due to a weather closure.  The lion's share of the rejects were featureless spectra consistent with FGK stars, or other unknown interlopers.  Some exhibited calcium triplet lines, for example.

@@

Based on the observed Na~I index alone, thirty-one sources (green boxes)in our survey are consistent with low surface gravity suggestive of youth.  The Na~I index is a pseudo eqvuivalent width.  We adopted the continuum and feature indices defined by \citet{2012AJ....143..114S}, a central wavelength $\lambda_c= 8190 \angstrom$ and measurement window $\delta \lambda = 22 \angstrom$.  We assigned an uncertainty $\sigma_{EW}$ to the equivalent width by adding in quadrature the uncertainty in the mean of the feature and continuum values.  We defined a Na~I youth detection as 3$\sigma_{EW}$ below the bottom 10\% of Na~I equivalent width values of RIZzo dwarfs for a given spectral type.  The 10\% boundary is shown as a solid line in Figure \ref{fig_NaI_EW}.  We also overplot the Na~I EWs of Beta Pic moving group members tabulated in \citet{2012AJ....143..114S}.  Our Na~I EW threshold cuts out some sources in the 10-20 Myr Beta Pic moving group \citep{2012AJ....143..114S} at spectral types M3 and earlier.  Therefore our Na~I EW threshold is overly restrictive at early spectral types.  We also compared the Na~I EWs for our sample to those for members of Upper Scorpius \citep{2006AJ....131.3016S}.  We converted the ratio computed in their Table 1 to an equivalent width, and found a range of about 0.6$-$4.2 $\angstrom$ for spectral types M5 to M8, comparable to the range we see.

@@

\subsection{Extinction and position in the HR Diagram}
\label{sec_HRD}
Equipped with derived effective temperatures and luminosities, we placed all 71 late type sources on an HR diagram.  Figure \ref{fig_HRD_NaI_Ex} shows the HR diagram with the pre-main sequence (PMS) evolutionary model tracks of \citep{1998A&A...337..403B,2002A&A...382..563B}.  The dotted lines are logarithmically spaced model isochrones from 1 Myr to 1 Gyr.  The solid black lines show the evolutionary track for sources down to 20 $M_{Jup}$.  The key idea from this Figure is that our sample is split into two populations- those below the main sequence and those above the main sequence.  Below the main sequence, sources are likely to be more distant background dwarfs.  Alternatively, a source can have a position in the HR diagram below the main sequence if it has a nearly edge-on disk.  These sources would have evidence for a mid-IR excess.  Sources OPH\_349 and OPH\_2 are potential edge-on disk sources.  Sources above the main sequence could also possibly be in the foreground, so membership assignment also requires evidence of low surface gravity from the optical spectroscopy.  Tables \ref{tbl_members_phot} and \ref{tbl_members_phot_mid_IR} list the near-IR photometry and mid-IR photometry for the 16 sources that we define as members.  Table \ref{tbl_members_phys} lists their derived properties.

@@

We explored the diversity of mid-IR excess emission properties by constructing spectral energy distributions (SEDs).  Figures \ref{fig_SEDs_9panel} and \ref{fig_SEDs_7panel} show the SEDs for the 16 members in our sample.  Many of the sources identified as young, low-mass objects do not appear to have mid-IR excess, despite meeting the disk criterion for selection.  Often, such sources met the selection criterion because they were detected at 24 $\mu$m.  When designing the survey, we targeted the lowest luminosity young brown dwarfs, which should not have detectable photospheres at 24 $\mu$m at the distance of Ophiuchus.  The sources we detected are warmer and more luminous than our targets, so we can detect photospheric 24 $\mu$m emission in some of them.

\begin{figure}[ht!]
  \caption[Spectral energy distributions of nine members of \emph{Ophiuchus}]{Spectral energy distributions of 9 members with spectral types M5$-$M6.  The gray circles show the observed photometry.  The green squares show the photometry corrected for the extinction value derived from the first-pass spectral typing.  Both the observed and extinction-corrected photometric data have been normalized by the extinction-corrected $H-$band measurement.  The red dotted line shows the blackbody with temperature equal to $T_{\mathrm{eff}}$ for each source.  \label{fig_SEDs_9panel} }
\centering
\includegraphics[scale=0.5]{chIMACS/figures/SEDS_9panel}
\end{figure}

@@

\begin{figure}[ht!]
\caption[IMACS spectra of 10 very low mass YSOs or young brown dwarfs towards \emph{Ophiuchus} with spectral types M5-M6]{IMACS spectra of 10 very low mass YSOs or young brown dwarfs towards \emph{Ophiuchus} with spectral types M5-M6.  The sources all demsontrate spectroscopic evidence of youth evinced by their weak Na~I feature at 8200$\angstrom$.  Source 2mx\_10919 is missing the Na~I feature but demonstrates exceptionally large H$\alpha$ attributable to accretion.  The spectra have been Gaussian smoothed with a 7$\angstrom$ kernel bandwidth.  All spectra were corrected for telluric absorption.  The spectra are normalized at 7500 $\angstrom$ and offset by 1 in the vertical direction. \label{fig_IMACS_spectra1} }
\centering
\includegraphics[scale=0.65]{chIMACS/figures/IMACS_spectra_M0_M6}
\end{figure}

@@

2mx\_9647 is the earliest spectral type source that meets either of our youth criteria.  It is consistent with a spectral type earlier than M1.  We assign it an M0 spectral type, though it could be a late K type.  There is no evidence of accretion, and the source does not have evidence for mid-IR excess.  The source is above the main sequence and demonstrates an $A_V$ of 3.8, so we reject the interpretation that it is a foreground object.  Still, we cannot confidently assign evidence of youth based on the spectrum, so we mark this source as a candidate.  Its telluric-corrected spectrum looks notably different from the comparison spectra which were not telluric-corrected.

@@

\subsection{Edge-on disks}
Figures \ref{fig_SEDs_9panel} and \ref{fig_SEDs_7panel} include the conspicuously rising SEDs of sources OPH\_349 and OPH\_2.  These sources demonstrate mid-IR flux increasing with wavelength from 3.6 to 24 $\mu$m.  The sources fall below the the main sequence in the HR diagram, indicating that these sources are most likely heavily-extincted edge-on disks with near-IR colors determined by a mixture of scattering and extinction.  The IMACS spectrum of OPH\_2 shows strong H$\alpha$ emission.  OPH\_349 is separated by 4" from OPH26571.  Below is the postage stamp images of the pair in different bands.  \cite{2008ApJ...683..822J} identified OPH\_349 during their search for deeply embedded YSOs.  This source is included in their list of candidate edge-on disks, since it exhibited very red mid-IR colors but no associated SCUBA flux.

\begin{figure}[ht!]
  \caption[Images of an edge-on disk source with nearby source]{Images of OPH\_349 with the nearby OPH\_26571.  Images are from right to left: MOSAIC $I-$band, $[3.6]$, $[8.0]$.}
\begin{minipage}[b]{0.3\linewidth}
\centering
\includegraphics[scale=0.15]{chIMACS/figures/OPH_349_I_image}
\end{minipage}
\hspace{0.5cm}
\begin{minipage}[b]{0.3\linewidth}
\centering
\includegraphics[scale=0.15]{chIMACS/figures/OPH_349_IRAC1_image}
\end{minipage}
\hspace{0.5cm}
\begin{minipage}[b]{0.3\linewidth}
\centering
\includegraphics[scale=0.15]{chIMACS/figures/OPH_349_IRAC4_image}
\end{minipage}
\end{figure}

@@

\subsection{Prospects for future surveys}
Given all the challenges and biases associated with photometric selection, it is instructive to ask ``What is the prospect for improving selection strategies in future surveys?''  The best possible strategy would be to have high precision proper motions and parallaxes to kinematically peg sources to the cloud of interest.  Parallaxes would be even better for deriving accurate luminosities, which would constrain ages and masses even better than we can now.  Unfortunately these low luminosity, red sources are below the detection threshold for \emph{GAIA}.  Proper motions with \emph{Spitzer} are just becoming available, given the long baseline (almost 10 years) from the c2d mission to the present day \citep{2012sptz.prop90071K}.

@@

Our survey was \emph{exceptionally} sensitive to very low luminosity substellar objects and yet we did not find them.  At face value this result would point to an intrinsic paucity of these sources, as expected from the decreasing number densisty with lower mass of the sub stellar initial mass function.  However, as the IMF is decreasing, the number of contaminating sources is increasing as photometric depth increases.  So the \emph{a-priori} probability that any given sources is a young brown dwarf goes down as a function of flux.  We only searched 1\% of the sources in our photometric catalog.  It is conceivable that we have missed very low luminosity brown dwarfs.  If we assume the peak of the IMF is around M5 for this off-core region of \emph{Ophiuchus}, and assume a star to brown dwarf ratio of 4, and assume we have detected all 7 of the M5's towards this region, we would expect zero L0 sources \citep{2012ARA&A..50...65L}.  The non-discovery of young L-type sources is consistent with---though not necessarily evidence for---a steeply declining IMF.  We do not find \emph{any} sources with spectral types later than M8.5, despite our ability to detect them.  To demonstrate that ability, Figure \ref{fig_luminosity_dist} shows the distributions of derived luminosities for all 71 of the sources demonstrating M or L spectral types, overplotted with the distributions of the confirmed young objects.

@@

\subsection{Is there a higher incidence of edge-on disks in BDs?}
One main result of this work is the discovery and identification of two edge-on disks around low-mass sources, out of only 5 disk-bearing sources towards this region of \emph{Ophiuchus}.  Forty percent of the disks are edge-on.  This fraction is higher than the incidence of edge-on disks around higher mass stars.  We interpret this high fraction has tentative evidence that brown dwarf disks have a larger scale height for a given radial position.  This interpretation is consistent with our intuition that the vertical component of gravity should be much lower for a given radial position, and that the disk orientation should be isotropic on the sky.  Of course, the achieved scale height also depends on the degree of turbulence in the disk, so a detailed analysis would have to consider the average temperature and diffusion timescales at a given location in the disk \citep{2012A&A...539A...9M,2009MNRAS.394L.141E}.  However, \emph{on average}, the systematic bias should tend towards higher gravitational scale height for brown dwarf disks, at a given radial distance.

@@

We have reported on a broad-band survey aimed at the discovery of young brown dwarfs and very low mass stars towards the \emph{Ophiuchus} star forming region.  We present the selection, spectral analysis, discovery, spectral types, luminosities, and physical characterization of a population of 12 young members, and 3 candidates of an off-core region towards \emph{Ophiuchus}.  Five of the 12 members show disks, while the other 7 members and 3 candidates show photospheric mid-IR colors.  All members show strong evidence for youth through their gravity-sensitive spectral features.  Specifically the Na~I lines are comparable to 1-3 Myr Taurus and Cha I members reported by Luhman and collaborators.  We interpret the majority of these photospheric young sources towards \emph{Ophiuchus} as Class III analogs- diskless young brown dwarfs that have already accreted their disks.  The prevalence of these sources is tantalizing evidence for a shorter-lived disk lifetime for very low mass stars and brown dwarfs than had been previously thought.  This shorter disk lifetime for brown dwarfs would put brown dwarf disk lifetimes more in line with their higher mass T-Tauri star counterparts.  We also take the prevalence of Class III analogs in this study compared to other studies as evidence for a possible bias in selection for sources with evidence for mid-IR excess.  This bias would manifest as an underestimated brown dwarf to star number density ratio, and an over-estimated disk lifetime.  Our key tool in avoiding this bias is the introduction of a custom filter that isolates late type sources from the large number of reddened contaminants.  This work lends modest support for an overall higher ratio of brown dwarfs to stars than had previously been thought.  We caution that contamination from Upper Scorpius could decrease the effect size seen here, but anticipate changes of merely a few objects, based on the low surface number density of Upper Sco.

>>>>

Of the 530 slits on the seven slit masks (Table \ref{tbl_IMACSslitMasks}), 505 spectra passed through spectral reduction with \texttt{Cosmos}.  The other 25 were not reduced mostly because they fell on chip gaps or were irretrievable.

@@

\subsection{Spectral classification with \emph{The Hammer}}
We visually inspected the IMACS $I-$band spectra for evidence of broad-band molecular absorption in the region $6500<\lambda(\angstrom)<9000 $.  The broad FeH, VO, and TiO bands are characteristic of late M spectral types, and are conspicuous even in low resolution ($R\sim100$) low signal-to-noise ratio ($S/N > 5$) spectra.  To accelerate the process of visually classifying hundreds of spectra, we employed Version 1.2.5 of \emph{The Hammer} spectral typing code \citep{2007AJ....134.2398C,2011AJ....141...97W}.  \emph{The Hammer} first computes a machine spectral type based on several spectral type sensitive indices.  Then \emph{The Hammer} overlays user-selectable comparison spectra, which can be visually matched to the overall spectral shape.  \emph{The Hammer} does not have a mechanism for tuning the extent of wavelength-dependent extinction, so since some of our sources are reddened, matches to the observed spectra may lead us to overestimate the spectral type.  This overestimate is okay, since we only use this first pass as a coarse filter for both signal-to-noise ratio ($S/N >5$), and overall spectral shape (consistent with M0 or later).  If the spectral shape is inconsistent with an M or L spectral type, we discard the spectrum from our follow up sample.  If there is evidence for an M or L spectral shape, we assign a coarse spectral type that we will later use to coarsely estimate the extinction.

@@

More than half of the spectra that were rejected had $S/N < 8$.  About 5 of these rejects were due to the most egregious cases of instrumental artifacts in the MOS spectral mapping.  In those cases, we went back to visually inspect the 2D trace to convince ourselves that the traces were inconsistent with M or L spectral types.  Slitmask \texttt{ophwes} (Table \ref{tbl_IMACSslitMasks}) exhibited a large fraction of unusable spectra since since it only received $\sim45$ minutes of on-sky observing time due to a weather closure.  The lion's share of the rejects were spectra consistent with FGK stars (evinced by calcium triplet lines), or unknown interlopers.

@@

Based on the observed Na~I index alone, thirty-one sources (green boxes)in our survey are consistent with low surface gravity suggestive of youth.  We adopted the continuum and feature indices defined by \citet{2012AJ....143..114S}, a central wavelength $\lambda_c= 8190 \angstrom$ and measurement window $\delta \lambda = 22 \angstrom$.  We assigned an uncertainty $\sigma_{EW}$ to the equivalent width by adding in quadrature the uncertainty in the mean of the feature and continuum values.  We defined a Na~I youth detection as 3$\sigma_{EW}$ below the bottom 10\% of Na~I equivalent width values of RIZzo dwarfs for a given spectral type.  The 10\% boundary is shown as a solid line in Figure \ref{fig_NaI_EW}.  We also overplot the Na~I EWs of Beta Pic moving group members tabulated in \citet{2012AJ....143..114S}.  Our Na~I EW threshold cuts out some sources in the 10-20 Myr Beta Pic moving group \citep{2012AJ....143..114S} at spectral types M3 and earlier.  Our spectra demonstrated a range of spectral types from M0 to L0.  The Na~I EW is ineffective at distinguishing gravity for M0 to M3 at our spectral resolution.  We also compared the Na~I EWs for our sample to those for members of Upper Scorpius \citep{2006AJ....131.3016S}.  We converted the ratio computed in their Table 1 to an equivalent width, and found a range of about 0.6$-$4.2 $\angstrom$ for spectral types M5 to M8, comparable to the range we see.

@@

\subsection{Extinction and position in the HR Diagram}
\label{sec_HRD}
Equipped with derived effective temperatures and luminosities, we placed all 71 late type sources on an HR diagram.  Figure \ref{fig_HRD_NaI_Ex} shows the HR diagram with the pre-main sequence (PMS) evolutionary model tracks of \citep{1998A&A...337..403B,2002A&A...382..563B}.  The dotted lines are logarithmically spaced model isochrones from 1 Myr to 1 Gyr.  The solid black lines show the evolutionary track for sources down to 20 $M_{Jup}$.  The key idea from this Figure is that our sample is split into two populations- those below the main sequence and those above the main sequence.  Below the main sequence, sources are likely to be more distant background dwarfs.  Alternatively, a source can have a position in the HR diagram below the main sequence if it has a nearly edge-on disk.  These sources would have evidence for a mid-IR excess.  Sources OPH\_349 and OPH\_2 are potential edge-on disk sources.  Sources above the main sequence could also possibly be in the foreground, so membership assignment also requires evidence of low surface gravity from the optical spectroscopy.  We define 16 sources define as members, based on a holistic review of each object in terms of its position on the HR diagram, indication of extinction, evidence of strong H$\alpha$ emission, previous characterizations from the literature, presence of mid-IR excess emission indicative of a disk, and presence of weak Na~I EW.  The holistic approach means that all pieces of available evidence were considered together, and membership was decided taking into account missing or noisy data.  Tables \ref{tbl_members_phot} and \ref{tbl_members_phot_mid_IR} list the near-IR photometry and mid-IR photometry for the 16 sources that we define as members.  Table \ref{tbl_members_phys} lists their derived properties.

@@

We explored the diversity of mid-IR excess emission properties by constructing spectral energy distributions (SEDs).  Figures \ref{fig_SEDs_9panel} and \ref{fig_SEDs_7panel} show the SEDs for the 16 members in our sample.  Many of the sources identified as young, low-mass objects do not appear to have mid-IR excess, despite meeting the disk criterion for selection.  Often, such sources met the selection criterion because they were detected at 24 $\mu$m.  When designing the survey, we targeted the lowest luminosity young brown dwarfs, which should not have detectable photospheres at 24 $\mu$m at the distance of Ophiuchus.  The sources we detected are typically warmer and more luminous than our prediction for M8 sources, so we can detect photospheric 24 $\mu$m emission in some of them.

\begin{figure}[ht!]
  \caption[Spectral energy distributions of nine members of \emph{Ophiuchus}]{Spectral energy distributions of 9 members with spectral types M5$-$M6.  The gray circles show the observed photometry.  The green squares show the photometry corrected for the extinction value derived from the first-pass spectral typing.  Both the observed and extinction-corrected photometric data have been normalized by the extinction-corrected $H-$band measurement.  The red dotted line shows the blackbody with temperature equal to $T_{\mathrm{eff}}$ for each source.  The observed photometry is sometimes below the blackbody photosphere, since the photospheric spectra for the cool sources differ substantially from blackbody sue to molecular species in their atmospheres.  \label{fig_SEDs_9panel} }
\centering
\includegraphics[scale=0.5]{chIMACS/figures/SEDS_9panel}
\end{figure}

@@

\begin{figure}[ht!]
\caption[IMACS spectra of 10 very low mass YSOs or young brown dwarfs towards \emph{Ophiuchus} with spectral types M5-M6]{IMACS spectra of 10 very low mass YSOs or young brown dwarfs towards \emph{Ophiuchus} with spectral types M5-M6.  The spectra have been Gaussian smoothed with a 7$\angstrom$ kernel bandwidth.  All spectra were corrected for telluric absorption.  The spectra are normalized at 7500 $\angstrom$ and offset by 1 in the vertical direction. \label{fig_IMACS_spectra1} }
\centering
\includegraphics[scale=0.6]{chIMACS/figures/IMACS_spectra_M0_M6}
\end{figure}

@@

2mx\_9647 is the earliest spectral type source that meets either of our youth criteria.  It is consistent with a spectral type earlier than M1.  We assign it an M0 spectral type, though it could be a late K type.  There is no evidence of accretion, and the source does not have evidence for mid-IR excess.  The source is above the main sequence and demonstrates an $A_V$ of 3.8, so we reject the interpretation that it is a foreground object.  Still, we cannot confidently assign evidence of youth based on the spectrum, so we mark this source as a candidate.

@@

\subsection{Edge-on disks}
Figures \ref{fig_SEDs_9panel} and \ref{fig_SEDs_7panel} include the conspicuously rising SEDs of sources OPH\_349 and OPH\_2.  These sources demonstrate mid-IR flux increasing with wavelength from 3.6 to 24 $\mu$m.  The sources fall below the the main sequence in the HR diagram, indicating that these sources are most likely heavily-extincted edge-on disks with near-IR colors determined by a mixture of scattering and extinction.  The IMACS spectrum of OPH\_2 shows strong H$\alpha$ emission.  OPH\_349 is separated by 4" from OPH26571.  Figure \ref{fig_OPH_349_pair} shows the postage stamp images of the pair in different bands.  \cite{2008ApJ...683..822J} identified OPH\_349 during their search for deeply embedded YSOs.  This source is included in their list of candidate edge-on disks, since it exhibited very red mid-IR colors but no associated SCUBA flux.

\begin{figure}[ht!]
  \caption[Images of an edge-on disk source with nearby source]{Images of OPH\_349 with the nearby OPH\_26571.  Images are from right to left: MOSAIC $I-$band, $[3.6]$, $[8.0]$. \label{fig_OPH_349_pair}}
\begin{minipage}[b]{0.3\linewidth}
\centering
\includegraphics[scale=0.15]{chIMACS/figures/OPH_349_I_image}
\end{minipage}
\hspace{0.5cm}
\begin{minipage}[b]{0.3\linewidth}
\centering
\includegraphics[scale=0.15]{chIMACS/figures/OPH_349_IRAC1_image}
\end{minipage}
\hspace{0.5cm}
\begin{minipage}[b]{0.3\linewidth}
\centering
\includegraphics[scale=0.15]{chIMACS/figures/OPH_349_IRAC4_image}
\end{minipage}
\end{figure}

@@

\subsection{Prospects for future surveys}
Given all the challenges and biases associated with photometric selection, it is instructive to ask ``What is the prospect for improving selection strategies in future surveys?''  The best possible strategy would be to have high precision proper motions and parallaxes to kinematically peg sources to the cloud of interest.  Parallaxes would be even better for deriving accurate luminosities, which would constrain ages and masses even better than we can now.  These low luminosity, red sources are below the detection threshold for \emph{GAIA}, but ground-based infrared parallax programs could detect parallax for them.  Proper motions with \emph{Spitzer} are just becoming available, given the long baseline (almost 10 years) from the c2d mission to the present day \citep{2012sptz.prop90071K}.

@@

Our survey was \emph{exceptionally} sensitive to very low luminosity substellar objects and yet we did not find them.  To demonstrate the survey depth, Figure \ref{fig_luminosity_dist} shows the distributions of derived luminosities for all 71 of the sources demonstrating M or L spectral types, overplotted with the distributions of the confirmed young objects.  At face value this result would point to an intrinsic paucity of these sources, as expected from the decreasing number densisty with lower mass of the sub stellar initial mass function.  However, as the IMF is decreasing, the number of contaminating sources is increasing as photometric depth increases.  So the \emph{a-priori} probability that any given source is a young brown dwarf goes down as a function of flux.  We only searched 1\% of the sources in our photometric catalog.  It is conceivable that we have missed very low luminosity brown dwarfs.  If we assume the peak of the IMF is around M5 for this off-core region of \emph{Ophiuchus}, and assume a star to brown dwarf ratio of 4, and assume we have detected all 7 of the M5's towards this region, we would expect zero L0 sources \citep{2012ARA&A..50...65L}.  The non-discovery of young L-type sources is consistent with---though not necessarily evidence for---a steeply declining IMF.  We do not find \emph{any} sources with spectral types later than M8.5, despite our ability to detect them.

@@

\subsection{Is there a higher incidence of edge-on disks in BDs?}
One main result of this work is the discovery and identification of two edge-on disks around low-mass sources, out of only 5 disk-bearing sources towards this region of \emph{Ophiuchus}.  Forty percent of the disks are edge-on.  This fraction is higher than the incidence of edge-on disks around higher mass stars.  We interpret this high fraction as tentative evidence that brown dwarf disks have a larger scale height for a given radial position.  This interpretation is consistent with our intuition that the vertical component of gravity should be much lower for a given radial position, and that the disk inclination should be random on the sky.  Of course, the achieved scale height also depends on the degree of turbulence in the disk, so a detailed analysis would have to consider the average temperature and diffusion timescales at a given location in the disk \citep{2012A&A...539A...9M,2009MNRAS.394L.141E}.  However, \emph{on average}, the systematic bias should tend towards higher gravitational scale height for brown dwarf disks, at a given radial distance.

@@

We have reported on a broad-band survey aimed at the discovery of young brown dwarfs and very low mass stars towards the \emph{Ophiuchus} star forming region.  We present the selection, spectral analysis, discovery, spectral types, luminosities, and physical characterization of a population of 12 young members, and 3 candidates of an off-core region towards \emph{Ophiuchus}.  Five of the 12 members show disks, while the other 7 members and 3 candidates show photospheric mid-IR colors.  All members show strong evidence for youth through their gravity-sensitive spectral features.  Specifically the Na~I lines are comparable to 1-3 Myr Taurus and Cha I members reported by Luhman and collaborators.  We interpret the majority of these photospheric young sources towards \emph{Ophiuchus} as Class III analogs- diskless young brown dwarfs that have already lost--or never had--disks.  The prevalence of these sources is tantalizing evidence for a shorter-lived disk lifetime for very low mass stars and brown dwarfs than had been previously thought.  This shorter disk lifetime for brown dwarfs would put brown dwarf disk lifetimes more in line with their higher mass T-Tauri star counterparts.  We also take the prevalence of Class III analogs in this study compared to other studies as evidence for a possible bias in selection for sources with evidence for mid-IR excess.  This bias would manifest as an underestimated brown dwarf to star number density ratio, and an over-estimated disk lifetime.  Our key tool in avoiding this bias is the introduction of a custom filter that isolates late type sources from the large number of reddened contaminants.  We caution that contamination from Upper Scorpius could decrease the effect size seen here, but anticipate changes of merely a few objects, based on the low surface number density of Upper Sco.
